Supermassive black hole and host bulge affairs \\ I. True to life, physically motivated galaxy decomposition

### 2015-07-10 papers/data_paper/datapaper.tex
fri

\title{Supermassive black hole and host bulge affairs \\ I. True to life, physically motivated galaxy decomposition.}

\author{G. A. D. Savorgnan and A. W. Graham}
\affil{Centre for Astrophysics and Supercomputing, Swinburne University of Technology, Hawthorn, Victoria 3122, Australia.}
\email{gsavorgn@astro.swin.edu.au}

@@

%% Mark off your abstract in the ``abstract'' environment. In the manuscript
%% style, abstract will output a Received/Accepted line after the
%% title and affiliation information. No date will appear since the author
%% does not have this information. The dates will be filled in by the
%% editorial office after submission.

\begin{abstract}
abstract % 2d worse than 1d say it!!!
\end{abstract}

\keywords{keywords}

@@

{\bf Rusli has explored the black hole - core relation.}

@@

In addition, \cite{lasker2014anal} {\bf who did not work at 3.6um} 

@@

\subsubsection{1D PSF}
A universal, average, one-dimensional Point Spread Function was characterized using the IRAF task {\tt imexamine}.
A nonlinear least squares \citep{moffat1969} profile\footnote{The \citep{moffat1969} profile 
has the following form:
\begin{equation}
\mu = \mu_{\rm 0} - 2.5 \log \Biggl[ 1 + \biggl( \frac{R}{\alpha} \biggr)^2 \Biggr]^{-\beta} ,
\end{equation}
where $R$ is the projected galaxy radius, $\mu_{\rm 0}$ is the central surface brightness, and 
$\alpha$ and $\beta$ regulate the width and the shape of the profile.} 
of fixed center and zero background was fit to the 
(background subtracted) pixels of 20 bright stars, belonging to different image mosaics.
%We employed both a Gaussian and a Moffat \citep{moffat1969} profile. 
The best-fit parameters of the 20 stars were then averaged together. 
Doing so, we obtained %$FWHM = 2''.03$ for the Gaussian function,
$(\alpha, \beta) = (2''.38, 4.39)$ %for the Moffat function
(see Appendix \ref{sec:app1} for the analytical expressions of the Moffat function).

@@

\subsection{1D fitting routine}
The decomposition of the surface brightness profiles was performed with software written by G. Savorgnan.
This software can fit an observed surface brightness profile with any linear combination of 
a set of analytical functions (S\'ersic, exponential, Gaussian, Moffat, Ferrer, symmetric Gaussian ring etc. 
see Appendix \ref{sec:app1} for a description of the analytical form of these profiles).
At each iteration, 
the model is numerically convolved with a Moffat filter, to account for PSF effects, 
and then matched to the data.
The minimization routine is based on the Levenberg-Marquardt algorithm.
During the fit, we deliberately did not make use of any weighting scheme on the data points that constitute the 
surface brightness profile, 
although the use of a linearly and logarithmically sampled profile effectively represents a different weighting scheme.
The all too often over-looked {\bf ??} with (signal-to-noise)-based weighting schemes 
is that they immediately become an incorrectly biased weighting schemes when additional components are present but not modelled.
For example, fitting a S\'ersic model to what is actually a nucleated elliptical galaxy immediately {\bf ??} 
a (signal-to-noise)-based weighting scheme 
and results in S\'ersic parameters which describe the bulge less accurately than had no (signal-to-noise)-weighting been used.
While we have paid careful attention to the components in each galaxy, 
and more so than the studies upon which our work is building from,
this is an issue that warrants the non application of (signal-to-noise)-based weighting schemes.
What is best in theory is not always best in practice -- in this case, because theory does not allow for unknown additional components
that are modelled.

@@

  \onecolumngrid
  \subsection{individual galaxies}
  \label{sec:indgal}

  individual galaxies \\
  For each galaxy, we show a figure and a table. 
  The figure illustrates our 1D best-fit model and the galaxy isophotal parameters. 
  The left panels refer to the major-axis $R_{\rm maj}$, 
  while the right panels refer to the equivalent-axis $R_{\rm eq}$, 
  i.e.~the geometric mean of the major ($a$) and minor ($b$) axis ($R_{\rm eq} = \sqrt{ab}$).
  The top panels display the galaxy surface brightness ($\mu$) radial profiles obtained with a linear sampling. 
  The black points are the observed data.  
  The color lines represent the individual (PSF-convolved) model components:
  red=S\'ersic, dark blue=exponential, green=Gaussian, cyan=Ferrer, gray=Gaussian ring, pink=PSF. 
  The best-fit parameters for the S\'ersic bulge model are inset.
  The total (PSF-convolved) model is shown with a black dashed line. 
  The residual profile ($data - model$) is shown as $\Delta \mu$ in the second row.
  The horizontal grey dashed line corresponds to an intensity 
  equal to three times the root mean square of the sky background fluctuations ($3 \times RMS_{\rm sky}$).
  $\Delta$ denotes the rms scatter of the fit in units of $\rm mag~arcsec^{-2}$.
  The lower six panels show the ellipticity ($\epsilon$), position angle ($PA$) and fourth harmonic ($B4$) radial profiles. \\
  The table reports a comparison between our results (from both our 1D and 2D decompositions) and those obtained by the following authors: 
  GD07 = \citeauthor{grahamdriver2007} (\citeyear{grahamdriver2007}, who performed 1D fits along the major-axis), 
  L+10 = \citeauthor{laurikainen2010} (\citeyear{laurikainen2010}, who performed 2D fits), 
  S+11 = \citeauthor{sani2011} (\citeyear{sani2011}, who performed 2D fits), 
  B+12 = \citeauthor{beifiori2012} (\citeyear{beifiori2012}, who performed 2D fits), 
  V+12 = \citeauthor{vika2012} (\citeyear{vika2012}, who performed 2D fits), 
  R+13 = \citeauthor{rusli2013} (\citeyear{rusli2013}, who performed 1D fits along the equivalent-axis),
  and L+14 = \citeauthor{lasker2014data} (\citeyear{lasker2014data}, who performed 2D fits).
  Each galaxy model is the sum of its individual components, which are expressed with the following nomenclature: (analytic function)-(physical component).
  The analytic functions can be: S=S\'ersic, e=exponential, G=Gaussian, F=Ferrer, M=Moffat and PSF.
  The physical components can be: bul=bulge or spheroid, d=disk, id=inner disk, bar, n=nucleus, l=lens or oval, r=ring, halo and spiral arms. 
  When a nuclear component or a partially depleted core have been masked, we signal them as ``m-n'' and ``m-c'', respectively.
  For example, the model ``S-bul + e-d + e-id + m-n + G-r'' reads ``S\'ersic-bulge + exponential-disk + exponential-inner disk + mask-nucleus + Gaussian-ring''. 
  The core-S\'ersic model used by \cite{rusli2013} is always implicitly associated with the galaxy spheroidal component. 
  When fitting their galaxy light profiles, \citeauthor{grahamdriver2007} excluded the innermost data points. 
  Their models implicitly include ``m-n'' or ``m-c''. 
  In the table caption, we comment on the most significant discrepancies between our results and those obtained by the other studies.

@@

  \begin{table}[h]
  \small
  \caption{Best-fit parameters for the spheroidal component of IC 1459.}
  \begin{center}
  \begin{tabular}{llcc}
  \hline
  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
    &  &  $[\rm arcsec]$ & \\
  \hline
  T.W. 1D maj. & S-bul + m-c & $63.1$  &  $6.6$ \\
  T.W. 1D eq.  & S-bul + m-c & $57.3$  &  $7.0$ \\
  T.W. 2D      & S-bul + m-c & $87.5$  &  $8.3$ \\
  \hline
  S+11         & S-bul + G-n   & $61.1$  &  $6.0$ \\
  R+13         & core-S\'ersic & $45.4$  &  $7.6$ \\
  L+14         & S-bul + m-c   & $62.4$  &  $8.3$ \\
  \hline
  \end{tabular}
  \end{center}
  \label{tab:ic1459}
  \tablecomments{S+11 obtained the smallest estimate of the S\'ersic index because they fit a nuclear component rather than masking the core. 
  R+13 obtained the smallest estimate of the effective radius 
  because they fit a circularized light profile that only extends out to $R_{\rm eq} \lesssim 60''$. }
  \end{table}

@@

  \begin{table}[h]
  \small
  \caption{Best-fit parameters for the spheroidal component of IC 4296.}
  \begin{center}
  \begin{tabular}{llcc}
  \hline
  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
    &  &  $[\rm arcsec]$ & \\
  \hline
  T.W. 1D maj. & S-bul + m-c & $65.9$  &  $5.8$ \\
  T.W. 1D eq.  & S-bul + m-c & $68.1$  &  $6.2$ \\
  T.W. 2D      & S-bul + m-c & $82.3$  &  $6.6$ \\
  \hline
  S+11         & S-bul + G-n & $33.6$  &  $4.0$ \\
  L+14         & S-bul + m-c & $97.8$  &  $8.2$ \\
  \hline
  \end{tabular}
  \end{center}
  \label{tab:ic4296}
  \tablecomments{
  S+11 obtained the smallest effective radius and S\'ersic index because they fit a nuclear component rather than masking the core. 
  L+14 obtained the largest effective radius and S\'ersic index, 
  although the 1D representation of their 2D fit (their Figure 8) shows that their model overestimates the galaxy light at large radii ($R_{\rm maj} > 100''$), 
  implying the need for a smaller $R_{\rm e}$ and $n$. 
  We suspect that this could be due to the pixel weighting scheme that they used.
  }
  \end{table}

@@

  \begin{table}[h]
  \small
  \caption{Best-fit parameters for the spheroidal component of M87.}
  \begin{center}
  \begin{tabular}{llcc}
  \hline
  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
    &  &  $[\rm arcsec]$ & \\
  \hline
  T.W. 1D maj. & S-bul + m-c  & $203.9$  &  $10.0$ \\
  T.W. 1D eq.  & S-bul + m-c  & $87.1$   &  $5.9$ \\
  T.W. 2D      & S-bul + m-c  & $88.3$   &  $4.3$ \\
  \hline
  GD07      & S-bul	    & $-$     &  $6.9$ \\
  S+11      & S-bul + G-n   & $99.5$  &  $4.0$ \\
  V+12      & S-bul + m-c   & $34.6$  &  $2.4$ \\
  R+13      & core-S\'ersic & $180.9$ &  $8.9$ \\
  L+14      & S-bul + m-c   & $122.0$ &  $5.6$ \\
  \hline
  \end{tabular}
  \end{center}
  \label{tab:m87}
  \tablecomments{
  The fit of R+13 returns the largest values for $R_{\rm e,sph}$ and $n_{\rm sph}$. 
  As in the case of M49, since their circularized light profile is almost three times more extended than ours, 
  it is possible that their best-fit model required a larger $R_{\rm e}$ to account for the extra intracluster halo light.
  V+12 obtained the smallest estimates of $R_{\rm e,sph}$ and $n_{\rm sph}$ because of the small radial extent of their data.
  }
  \end{table}

@@

  m87 has ellipticity still increasing, the halo is not prevailing
  m89 instead has a plateau in the ell prof, bcz the halo is predominant
  we need to fit the halo

@@

  Our equivalent-axis decomposition returns a spheroidal component accounting for 95\% of the total light,
  and an embedded disk accounting for the remaining 5\%.
  In passing, we note that the bulge-disk decomposition performed by \citet{rusli2011} on NGC 1332 
  is significantly different from our best-fit model.
  \citet{rusli2011} did not identify an intermediate-scale embedded disk, 
  but instead proposed a model featuring a S\'ersic bulge ($n_{\rm sph} \sim 2.3$, $R_{\rm e,sph} \sim 8''$), accounting for 43\% of the total light, 
  and a large-scale exponential disk. 
  This result led them to the conclusion that NGC 1332 is a disk dominated lenticular galaxy 
  and is displaced from the $M_{\rm BH} - L_{\rm K,sph}$ (black hole mass vs. $K$-band spheroid luminosity) relation of \citet{marconihunt2003} 
  by an order of magnitude along the $M_{\rm BH}$ direction.
  Assuming instead that, as follows from our model, 
  the galaxy spheroid is a factor of two more luminous than what claimed by \citet{rusli2011}, 
  NGC 1332 would no longer be an outlier in our $M_{\rm BH} - L_{\rm sph}$ diagram. \\

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/n1332_1Dfit.eps}
  \caption{Best-fit model and isophotal parameters for NGC 1332.
  NGC 1332 is an edge-on elliptical/lenticular galaxy. 
  Given its large stellar velocity dispersion, this galaxy is expected to host a partially depleted core. 
  The ellipticity profile proves the presence of an intermediate-scale disk. 
  Given the edge-on inclination of such disk, we model it with a low-$n$ S\'ersic profile. 
  The data within the innermost $6''.1$ are excluded from the fit.
  }
  \end{center}
  \end{figure}

@@

  \begin{table}[h]
  \small
  \caption{Best-fit parameters for the spheroidal component of NGC 1399.}
  \begin{center}
  \begin{tabular}{llcc}
  \hline
  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
    &  &  $[\rm arcsec]$ & \\
  \hline
  T.W. 1D maj. & S-bul + m-c + e-id & $405.2$  &  $10.0$ \\
  T.W. 1D eq.  & S-bul + m-c + e-id & $338.1$  &  $10.0$ \\
  %T.W. 2D	&  & $$  & $$  &  $$ \\
  \hline
  GD07         & S-bul  		    & $-$      &  $16.8$ \\
  R+13         & core-S\'ersic + (S+e)-halo & $36.2$   &  $7.4$ \\
  L+14         & S-bul + m-c		    & $154.0$  &  $11.1$ \\
  \hline
  \end{tabular}
  \end{center}
  \label{tab:n1399}
  \tablecomments{
  R+13 used a combination of a S\'ersic + exponential profile to model the halo of this galaxy, 
  and obtained the smallest estimate of the effective radius, 
  which is at odds with the fact that central cluster galaxies typically have the largest sizes. 
  L+14 finds an effective radius which is a factor of two smaller than that obtained by us 
  because their data have a smaller radial extent ($R_{\rm maj} \lesssim 130'$). 
  }
  \end{table}

@@

  \begin{table}[h]
  \small
  \caption{Best-fit parameters for the spheroidal component of NGC 3115.}
  \begin{center}
  \begin{tabular}{llcc}
  \hline
  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
    &  &  $[\rm arcsec]$ & \\
  \hline
  T.W. 1D maj. & S-bul + e-d + G-r & $43.6$  &  $4.4$ \\
  T.W. 1D eq.  & S-bul + e-d + G-r & $34.4$  &  $5.1$ \\
  %T.W. 2D	&  & $$  & $$  &  $$ \\
  \hline
  %GD07         & ??? TBD	       & $-$	&  $13.0$ \\
  S+11         & S-bul + e-d	       & $27.1$ &  $3.0$ \\
  L+14         & S-bul + e-d + S-halo  & $3.9$  &  $3.0$ \\
  \hline
  \end{tabular}
  \end{center}
  \label{tab:n3115}
  \tablecomments{
  S+11 found a smaller effective radius and S\'ersic index for the spheroidal component of this galaxy, 
  possibly because they modelled the intermediate scale disk as a large-scale disk.
  L+14 also used a model with a bulge encased in a larger disk, and attributed the excess of light at large radii to a halo. 
  In doing so, they obviously obtained an even smaller bulge effective radius.
  }
  \end{table}

@@

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/n3227_1Dfit.eps}
  \caption{Best-fit model and isophotal parameters for NGC 3227.
  NGC 3227 is a spiral galaxy with a large-scale bar. 
  This galaxy hosts a Seyfert AGN \citep{khachikian1974} and circumnuclear dust \citep{martini2003}. 
  The large-scale bar produces an evident bump in the major-axis surface brightness profile,
  which is curiously absent in the equivalent-axis profile. 
  We model the bar with a Ferrer function and the nucleus with a Gaussian function. 
  As expected, the Ferrer component is rejected by the equivalent-axis fit. 
  }
  \end{center}
  \end{figure}

>>>>

\title{Supermassive black hole and host bulge affairs \\ I. True to life, physically motivated galaxy decomposition}

\author{G. A. D. Savorgnan and A. W. Graham}
\affil{Centre for Astrophysics and Supercomputing, Swinburne University of Technology, Hawthorn, Victoria 3122, Australia}
\email{gsavorgn@astro.swin.edu.au}

@@

\begin{abstract}
Several recent studies have performed galaxy decompositions 
to investigate correlations between the black hole mass and the host spheroid properties, 
but they have not converged to the same conclusions. 
This is because their best fit models for the same galaxy were often significantly different 
and not consistent with each other in terms of fitted components. 
Using $3.6 \rm ~\mu m$ \emph{Spitzer} imagery, which is a superb tracer of the stellar mass (superior to the $K$-band), 
we have performed state-of-the-art multicomponent decompositions for 66 galaxies 
with directly measured black hole masses. 
Our sample is the largest to date and, 
unlike previous studies, contains a large number (17) of spiral galaxies with low black hole masses. 
We paid careful attention to the image mosaicking, sky subtraction and masking of contaminating sources.
Thanks to a scrupulous inspection of the galaxy photometry (through isophotal analysis and unsharp masking) and -- for the first time -- of the 2D kinematics, 
we were able to identify and model bulges, large-scale, intermediate-scale or nuclear disks, bars, rings, spiral arms, halos, extended or unresolved nuclear 
sources and partially depleted cores. 
For each individual galaxy, we compared our best-fit model with those presented by the previous studies, 
explained the discrepancies and identified the optimal decomposition.
We independently performed 1D and 2D decompositions, 
and concluded that, at least when modelling large, nearby galaxies, 1D techniques have more advantages than 2D techniques. 
Finally, we developed a method to estimate the uncertainties on the 1D best-fit parameters 
that takes into account systematic errors, 
unlike popular 2D codes that only consider statistical errors.

\end{abstract}

\keywords{galaxies: bulges; galaxies: elliptical and lenticular, cD; galaxies: evolution; galaxies: structure; black hole physics}

@@

@@

In addition, \cite{lasker2014anal} 

@@

\subsubsection{1D PSF}
A universal, average, one-dimensional Point Spread Function was characterized using the IRAF task {\tt imexamine}.
A nonlinear least squares \citep{moffat1969} profile\footnote{The \citep{moffat1969} profile 
has the following form:
\begin{equation}
\mu = \mu_{\rm 0} - 2.5 \log \Biggl[ 1 + \biggl( \frac{R}{\alpha} \biggr)^2 \Biggr]^{-\beta} ,
\end{equation}
where $R$ is the projected radius, $\mu_{\rm 0}$ is the central surface brightness, and 
$\alpha$ and $\beta$ regulate the width and the shape of the profile.} 
of fixed center and zero background was fit to the 
(background subtracted) pixels of 20 bright stars, belonging to different image mosaics.
%We employed both a Gaussian and a Moffat \citep{moffat1969} profile. 
The best-fit parameters of the 20 stars were then averaged together. 
Doing so, we obtained %$FWHM = 2''.03$ for the Gaussian function,
$(\alpha, \beta) = (2''.38, 4.39)$.

@@

\subsection{1D fitting routine}
The decomposition of the surface brightness profiles was performed with software written by G. Savorgnan.
This software can fit an observed surface brightness profile with any linear combination of 
a set of analytical functions (S\'ersic, exponential, Gaussian, Moffat, Ferrer, symmetric Gaussian ring etc. 
see Appendix \ref{sec:app1} for a description of the analytical form of these profiles).
At each iteration, 
the model is numerically convolved with a Moffat filter, to account for PSF effects, 
and then matched to the data.
The minimization routine is based on the Levenberg-Marquardt algorithm.
During the fit, we deliberately did not make use of any weighting scheme on the data points that constitute the 
surface brightness profile, 
although the use of a linearly and logarithmically sampled profile effectively represents a different weighting scheme.
The all too often over-looked flaw with (signal-to-noise)-based weighting schemes 
is that they immediately become an incorrectly biased weighting schemes when additional components are present but not modelled.
For example, fitting a S\'ersic model to what is actually a nucleated elliptical galaxy immediately voids 
a (signal-to-noise)-based weighting scheme 
and results in S\'ersic parameters which describe the bulge less accurately than had no (signal-to-noise)-weighting been used.
While we have paid careful attention to the components in each galaxy, 
this is an issue that warrants the non application of (signal-to-noise)-based weighting schemes.
What is best in theory is not always best in practice -- in this case, because theory does not allow for unknown additional components
that are modelled.

@@

\acknowledgments
GS acknowledges the invaluable support received from Alessandro Marconi, Eleonora Sani and Leslie Hunt 
in the early stages of this research.
GS warmly thanks Chieng Peng, Peter Erwin, Luca Cortese, Giuseppe Gavazzi, 
Bililign Dullo, Paolo Bonfini, Elisabete Lima Da Cunha 
and Gonzalo Diaz 
for useful discussion. \\
This research was supported by Australian Research Council funding through grants
DP110103509 and FT110100263.
This work is based on observations made with the IRAC instrument \citep{fazio2004IRAC} 
on-board the Spitzer Space Telescope, 
which is operated by the Jet Propulsion Laboratory, 
California Institute of Technology under a contract with NASA.
This research has made use of the GOLDMine database \citep{goldmine} and the NASA/IPAC Extragalactic Database (NED) 
which is operated by the Jet Propulsion Laboratory, California Institute of Technology, 
under contract with the National Aeronautics and Space Administration.

  \onecolumngrid
  \subsection{Individual galaxy decompositions}
  \label{sec:indgal}

  For each galaxy, we show a figure and a table. 
  The figure illustrates our 1D best-fit model and the galaxy isophotal parameters. 
  The left panels refer to the major-axis $R_{\rm maj}$, 
  while the right panels refer to the equivalent-axis $R_{\rm eq}$, 
  i.e.~the geometric mean of the major ($a$) and minor ($b$) axis ($R_{\rm eq} = \sqrt{ab}$).
  The top panels display the galaxy surface brightness ($\mu$) radial profiles obtained with a linear sampling. 
  The black points are the observed data used in the fit and the empty points are the observed data excluded from the fit.  
  The color lines represent the individual (PSF-convolved) model components:
  red=S\'ersic, dark blue=exponential, green=Gaussian, cyan=Ferrer, gray=Gaussian ring, pink=PSF. 
  The best-fit parameters for the S\'ersic bulge model are inset.
  The total (PSF-convolved) model is shown with a black dashed line. 
  The residual profile ($data - model$) is shown as $\Delta \mu$ in the second row.
  The horizontal grey dashed line corresponds to an intensity 
  equal to three times the root mean square of the sky background fluctuations ($3 \times RMS_{\rm sky}$).
  $\Delta$ denotes the rms scatter of the fit in units of $\rm mag~arcsec^{-2}$.
  The lower six panels show the ellipticity ($\epsilon$), position angle ($PA$) and fourth harmonic ($B4$) radial profiles. \\
  The table reports a comparison between our results (from both our 1D and 2D decompositions) and those obtained by the following authors: 
  GD07 = \citeauthor{grahamdriver2007} (\citeyear{grahamdriver2007}, who performed 1D fits along the major-axis), 
  L+10 = \citeauthor{laurikainen2010} (\citeyear{laurikainen2010}, who performed 2D fits), 
  S+11 = \citeauthor{sani2011} (\citeyear{sani2011}, who performed 2D fits), 
  B+12 = \citeauthor{beifiori2012} (\citeyear{beifiori2012}, who performed 2D fits), 
  V+12 = \citeauthor{vika2012} (\citeyear{vika2012}, who performed 2D fits), 
  R+13 = \citeauthor{rusli2013} (\citeyear{rusli2013}, who performed 1D fits along the equivalent-axis),
  and L+14 = \citeauthor{lasker2014data} (\citeyear{lasker2014data}, who performed 2D fits).
  Each galaxy model is the sum of its individual components, which are expressed with the following nomenclature: (analytic function)-(physical component).
  The analytic functions can be: S=S\'ersic, e=exponential, G=Gaussian, F=Ferrer, M=Moffat and PSF.
  The physical components can be: bul=bulge (or spheroid), d=disk, id=inner disk, bar, n=nucleus, l=lens or oval, r=ring, halo and spiral arms. 
  When a nuclear component or a partially depleted core have been masked, we signal them as ``m-n'' and ``m-c'', respectively.
  For example, the model ``S-bul + e-d + e-id + m-n + G-r'' reads ``S\'ersic-bulge + exponential-disk + exponential-inner disk + mask-nucleus + Gaussian-ring''. 
  The core-S\'ersic model used by \cite{rusli2013} is always implicitly associated with the galaxy spheroidal component. 
  When fitting their galaxy light profiles, \citeauthor{grahamdriver2007} excluded the innermost data points. 
  Their models implicitly include ``m-n'' or ``m-c''. 
  In the table caption, we comment on the most significant discrepancies between our results and those obtained by the other studies.

@@

  \begin{table}[h]
  \small
  \caption{Best-fit parameters for the spheroidal component of IC 1459.}
  \begin{center}
  \begin{tabular}{llcc}
  \hline
  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
    &  &  $[\rm arcsec]$ & \\
  \hline
  T.W. 1D maj. & S-bul + m-c & $63.1$  &  $6.6$ \\
  T.W. 1D eq.  & S-bul + m-c & $57.3$  &  $7.0$ \\
  T.W. 2D      & S-bul + m-c & $87.5$  &  $8.3$ \\
  \hline
  S+11         & S-bul + G-n   & $61.1$  &  $6.0$ \\
  R+13         & core-S\'ersic & $45.4$  &  $7.6$ \\
  L+14         & S-bul + m-c   & $62.4$  &  $8.3$ \\
  \hline
  \end{tabular}
  \end{center}
  \label{tab:ic1459}
  %\tablecomments{S+11 obtained the smallest estimate of the S\'ersic index because they fit a nuclear component rather than masking the core. 
  %R+13 obtained the smallest estimate of the effective radius 
  %because they fit a circularized light profile that only extends out to $R_{\rm eq} \lesssim 60''$. }
  \end{table}

@@

  \begin{table}[h]
  \small
  \caption{Best-fit parameters for the spheroidal component of IC 4296.}
  \begin{center}
  \begin{tabular}{llcc}
  \hline
  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
    &  &  $[\rm arcsec]$ & \\
  \hline
  T.W. 1D maj. & S-bul + m-c & $65.9$  &  $5.8$ \\
  T.W. 1D eq.  & S-bul + m-c & $68.1$  &  $6.2$ \\
  T.W. 2D      & S-bul + m-c & $82.3$  &  $6.6$ \\
  \hline
  S+11         & S-bul + G-n & $33.6$  &  $4.0$ \\
  L+14         & S-bul + m-c & $97.8$  &  $8.2$ \\
  \hline
  \end{tabular}
  \end{center}
  \label{tab:ic4296}
  \tablecomments{
  S+11 obtained the smallest effective radius and S\'ersic index because they fit a nuclear component rather than masking the core. 
  %L+14 obtained the largest effective radius and S\'ersic index, 
  %although the 1D representation of their 2D fit (their Figure 8) shows that their model overestimates the galaxy light at large radii ($R_{\rm maj} > 100''$), 
  %implying the need for a smaller $R_{\rm e}$ and $n$. 
  %We suspect that this could be due to the pixel weighting scheme that they used.
  }
  \end{table}

@@

  \begin{table}[h]
  \small
  \caption{Best-fit parameters for the spheroidal component of M87.}
  \begin{center}
  \begin{tabular}{llcc}
  \hline
  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
    &  &  $[\rm arcsec]$ & \\
  \hline
  T.W. 1D maj. & S-bul + m-c  & $203.9$  &  $10.0$ \\
  T.W. 1D eq.  & S-bul + m-c  & $87.1$   &  $5.9$ \\
  T.W. 2D      & S-bul + m-c  & $88.3$   &  $4.3$ \\
  \hline
  GD07      & S-bul	    & $-$     &  $6.9$ \\
  S+11      & S-bul + G-n   & $99.5$  &  $4.0$ \\
  V+12      & S-bul + m-c   & $34.6$  &  $2.4$ \\
  R+13      & core-S\'ersic & $180.9$ &  $8.9$ \\
  L+14      & S-bul + m-c   & $122.0$ &  $5.6$ \\
  \hline
  \end{tabular}
  \end{center}
  \label{tab:m87}
  \tablecomments{
  The equivalent-axis fit of R+13 returns the largest values for $R_{\rm e,sph}$ and $n_{\rm sph}$. 
  As in the case of M49, since their circularized light profile is almost three times more extended than ours, 
  it is possible that their best-fit model required a larger $R_{\rm e}$ to account for the extra intracluster halo light.
  V+12 obtained the smallest estimates of $R_{\rm e,sph}$ and $n_{\rm sph}$ because of the small radial extent of their data.
  }
  \end{table}

@@

@@

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/n1332_1Dfit.eps}
  \caption{Best-fit model and isophotal parameters for NGC 1332.
  NGC 1332 is an edge-on elliptical/lenticular galaxy. 
  Given its large stellar velocity dispersion, this galaxy is expected to host a partially depleted core. 
  The ellipticity profile proves the presence of an intermediate-scale disk. 
  Given the edge-on inclination of such disk, we model it with a low-$n$ S\'ersic profile. 
  The data within the innermost $6''.1$ are excluded from the fit.
  Our equivalent-axis decomposition returns a spheroidal component accounting for 95\% of the total light,
  and an embedded disk accounting for the remaining 5\%.
  In passing, we note that the bulge-disk decomposition performed by \citet{rusli2011} on NGC 1332 
  is significantly different from our best-fit model.
  \citet{rusli2011} did not identify an intermediate-scale embedded disk, 
  but instead proposed a model featuring a S\'ersic bulge ($n_{\rm sph} \sim 2.3$, $R_{\rm e,sph} \sim 8''$), accounting for 43\% of the total light, 
  and a large-scale exponential disk. 
  This result led them to the conclusion that NGC 1332 is a disk dominated lenticular galaxy 
  and is displaced from the $M_{\rm BH} - L_{\rm K,sph}$ (black hole mass vs. $K$-band spheroid luminosity) relation of \citet{marconihunt2003} 
  by an order of magnitude along the $M_{\rm BH}$ direction.
  Assuming instead that, as follows from our model, 
  the galaxy spheroid is a factor of two more luminous than what claimed by \citet{rusli2011}, 
  NGC 1332 would no longer be an outlier in our $M_{\rm BH} - L_{\rm sph}$ diagram. \\
  }
  \end{center}
  \end{figure}

@@

  \begin{table}[h]
  \small
  \caption{Best-fit parameters for the spheroidal component of NGC 1399.}
  \begin{center}
  \begin{tabular}{llcc}
  \hline
  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
    &  &  $[\rm arcsec]$ & \\
  \hline
  T.W. 1D maj. & S-bul + m-c + e-id & $405.2$  &  $10.0$ \\
  T.W. 1D eq.  & S-bul + m-c + e-id & $338.1$  &  $10.0$ \\
  %T.W. 2D	&  & $$  & $$  &  $$ \\
  \hline
  GD07         & S-bul  		    & $-$      &  $16.8$ \\
  R+13         & core-S\'ersic + (S+e)-halo & $36.2$   &  $7.4$ \\
  L+14         & S-bul + m-c		    & $154.0$  &  $11.1$ \\
  \hline
  \end{tabular}
  \end{center}
  \label{tab:n1399}
  \tablecomments{
  R+13 used a combination of a S\'ersic + exponential profile to model the halo of this galaxy, 
  and obtained the smallest estimate of the effective radius, 
  which is at odds with the fact that central cluster galaxies typically have very large sizes. 
  L+14 finds an effective radius which is a factor of two smaller than that obtained by us 
  because their data have a smaller radial extent ($R_{\rm maj} \lesssim 130'$). 
  }
  \end{table}

@@

  \begin{table}[h]
  \small
  \caption{Best-fit parameters for the spheroidal component of NGC 3115.}
  \begin{center}
  \begin{tabular}{llcc}
  \hline
  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
    &  &  $[\rm arcsec]$ & \\
  \hline
  T.W. 1D maj. & S-bul + e-d + G-r & $43.6$  &  $4.4$ \\
  T.W. 1D eq.  & S-bul + e-d + G-r & $34.4$  &  $5.1$ \\
  %T.W. 2D	&  & $$  & $$  &  $$ \\
  \hline
  %GD07         & ??? TBD	       & $-$	&  $13.0$ \\
  S+11         & S-bul + e-d	       & $27.1$ &  $3.0$ \\
  L+14         & S-bul + e-d + S-halo  & $3.9$  &  $3.0$ \\
  \hline
  \end{tabular}
  \end{center}
  \label{tab:n3115}
  \tablecomments{
  L+14 used a model with a bulge encased in a larger disk, and attributed the excess of light at large radii to a halo. 
  In doing so, they obviously obtained a smaller bulge effective radius.
  }
  \end{table}

@@

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/n3227_1Dfit.eps}
  \caption{Best-fit model and isophotal parameters for NGC 3227.
  NGC 3227 is a spiral galaxy with a large-scale bar. 
  This galaxy hosts a Seyfert AGN \citep{khachikian1974} and circumnuclear dust \citep{martini2003}. 
  The large-scale bar produces an evident bump in the major-axis surface brightness profile,
  which is curiously absent in the equivalent-axis profile. 
  We model the bar with a Ferrer function and the nucleus with a Gaussian function. 
  The Ferrer component is rejected by the equivalent-axis fit. 
  }
  \end{center}
  \end{figure}

  \begin{table}[h]
  \small
  \caption{Best-fit parameters for the spheroidal component of NGC 3227.}
  \begin{center}
  \begin{tabular}{llcc}
  \hline
  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
    &  &  $[\rm arcsec]$ & \\
  \hline
  T.W. 1D maj. & S-bul + e-d + F-bar + G-n   & $8.1$  &  $1.7$ \\
  T.W. 1D eq.  & S-bul + e-d + [F-bar] + G-n & $4.6$  &  $1.1$ \\
  %T.W. 2D	&  & $$  & $$  &  $$ \\
  \hline
  L+04         & S-bul + e-d + F-bar & $1.8$  &  $2.2$ \\
  S+11         & S-bul + e-d	     & $82.9$ &  $4.0$ \\
  L+14         & S-bul + e-d + S-bar & $0.7$  &  $4.1$ \\
  \hline
  \end{tabular}
  \end{center}
  \label{tab:n3227}
  \tablecomments{
  The models of L+10 and L+14 do not account for the bright nulcear component, 
  and thus underestimate the bulge effective radius and overestimate the bulge S\'ersic index.
  The bulge effective radius obtained by S+11 is larger because they did not model the bar. 
  }
  \end{table}
